---
title: "Your first commit"
format: html
editor: visual
---

## The Readme.md

The README.md is often **the first item a visitor will see when visiting your repository**. README files typically include information on: What the project does and why the project is useful.

The ending .md is an indicator of the Markdown language. Markdown is a lightweight markup language that you can use to add formatting elements to plaintext text documents. The documents for this website are also written in Markdown.

Examples of the Markdown language:

## Headlines

The number of `#` determine the level of the headline:

    # A first level heading

    ## A second level heading

    ## A third level heading

# A first level heading

## A second level heading

### A third level heading

You can learn about the markdown language [here at this official resource](https://www.markdownguide.org/getting-started/) and at this [resource from Github](https://docs.github.com/en/get-started/writing-on-github/getting-started-with-writing-and-formatting-on-github/basic-writing-and-formatting-syntax).

> Challenge: Your first commit in markdown

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
